WIDS 2024 Final Project

### 2024-01-12 Code/R FIle.qmd
fixed regression graph labels

Graph of regression estimate by decade and year
```{r}
ggplot(CB_party_regression, aes(x = Decade, y = Estimate, fill = Region)) +
  geom_bar(stat = "identity", position = "dodge", color = ifelse(CB_party_regression$P_Value > 0.05, "black", NA), size = 0.2) +
  theme_minimal() +
  labs(title = "Linear Regression Estimate by Decade",
       subtitle = "Model of Percent Collective Bargaining vs Proportion of House Delegation That is Democratic")
```

>>>>

Graph of regression estimate by decade and year
```{r}
ggplot(CB_party_regression, aes(x = Decade, y = Estimate, fill = Region)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_text(aes(label = sprintf("P=%.3f", P_Value)),
             position = position_dodge(width = 0.9),
             vjust = -0.2,
             size = 3) +
  theme_minimal() +
  labs(title = "Linear Regression Estimate by Decade",
       subtitle = "Model of Percent Collective Bargaining vs Proportion of House Delegation That is Democratic")
```
